InteroceptionStudy_GPValidation

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

@@

# rm(tmp.df4_sum_fullt)
# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
# 
# tmp.df4_sum_fullt
```

@@

import biopac heart rate
```{r}
nrow(tmp.df4_sum_full_bio)

@@

# now read them

# old
db_biohr <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

@@

```{r}
library(readxl)
library(dplyr)
db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

View(db_HR_bio)

nrow(db_HR_bio)

db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]

@@

test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")

levels(as.factor(db_HR_bio$filename))
db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)

@@

db_HR_bio$`Stim-Response Analysis`

db_HR_bio$stim<- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)

@@

@@

test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
levels(as.factor(db_HR_biotest$ssid))

@@

db_HR_bio$trigger<- substr(db_HR_bio$stim, 10,13)

unique((as.numeric(db_HR_bio$trigger)-128))

@@

db_HR_bio$trigger<- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))

unique((as.numeric(db_HR_bio$trigger)))

@@

db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger< 100)

db_HR_bio1<- db_HR_bio1%>%
  arrange(as.numeric(timestart), ssid)

@@

#tno
#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
table(is.na(db_HR_bio1$ssid))
db_HR_bio1<- db_HR_bio1%>%
  arrange(as.numeric(timestart), ssid)

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(as.numeric(ssid))%>%
  mutate(tNo = -6:49)

db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 328)

db_HR_bio328<- db_HR_bio328 %>%
  group_by(as.numeric(ssid))%>%
  mutate(tNo = -6:24)

db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)

@@

levels(as.factor(db_HR_bio1no328$ssid))
db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`

#mereg old and new heart rate
# now read them
db_biohr$trigger

db_biohr$tno<-db_biohr$trigger
db_HR_bio2$trigger
colnames(db_biohr)

db_biohr$Mean_HR<- db_biohr$HR_BIO

db_biohr$timestart<- db_biohr$Time

left_join(db_HR_bio2, db_biohr)

@@

db_HR_bio2$`as.numeric(ssid)`<- NULL

str((db_HR_bio2))
str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

@@

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

@@

db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
db_biohrold2test$ssid<- NULL
db_HR_bio2$ssid<- NULL

@@

db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

db_HR_bio_final$ssid<- db_HR_bio_final$subj
levels(as.factor(db_HR_bio_final$ssid))

@@

@@

db_HR_bio1$tNo<- if_else(db_HR_bio1$tNo< 0, as.numeric(db_HR_bio1$tNo), as.numeric(db_HR_bio1$tNo+1))

db_HR_bio1$

@@

import biopac heart rate
```{r}
nrow(tmp.df4_sum_full_bio)

# now read them
db_biohr <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_biohr$Order<- NULL
db_biohr$filename<- NULL
db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
unique(tmp.df4_sum_full_bio$ssid)
unique(db_biohr$ssid)
tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))

db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
  geom_point()+
  geom_smooth(method = 'lm')
tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')

cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')

# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)

tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))

unique(tmp.df4_sum_full_bio_hr_stim$screencontent)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')

tmp.df4_sum_full_bio_hr_stim%>%
      group_by(ssid, IAS)%>%
      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
  summarise(new = cor(corr, IAS))
  # summarise_at(c('TAS'), mean)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

tmp.df4_sum_full_bio_hr_stim%>%
group_by(valence_cat)%>%
  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
  geom_point()+
  geom_smooth(method = 'lm')

@@

>>>>

db_parsed$screencontent_no <- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

@@

# rm(tmp.df4_sum_fullt)
# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
# 
# tmp.df4_sum_fullt

tmp.df4_sum_full
```

@@

import biopac heart rate
```{r}

nrow(tmp.df4_sum_full_bio)

@@

# now read them
# old
db_biohr <-
  list.files(pattern = "*.xls", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
library(readxl)
library(dplyr)
# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

# db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]

@@

# test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")

levels(as.factor(db_HR_bio$filename))

db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)

@@

# 
db_HR_bio$`Stim-Response Analysis`

# flag stimulus
db_HR_bio$stim <- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)

@@

db_HR_bio

@@

# test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
# levels(as.factor(db_HR_biotest$ssid))

@@

db_HR_bio$trigger <- substr(db_HR_bio$stim, 10,13)

# for soem reason this 
unique((as.numeric(db_HR_bio$trigger)-128))

@@

db_HR_bio$trigger2 <- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))

unique((as.numeric(db_HR_bio$trigger2)))

@@

db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)

db_HR_bio1<- db_HR_bio1%>%
  arrange(ssid, as.numeric(timestart))

@@

#tno
#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
table(is.na(db_HR_bio1$ssid))
# 
# db_HR_bio1<- db_HR_bio1%>%
#   arrange(as.numeric(timestart), ssid)

# use this

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<72)

db_HR_bio1no328<- db_HR_bio1no328 %>%
  arrange(ssid, trigger2)%>%
  filter(!duplicated(trigger2))

db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7)) #56 trials

unique(db_HR_bio1no328$tNo)

range(db_HR_bio1no328$tNo)

table(db_HR_bio1no328$tNo)

# test<- subset(db_HR_bio1no328, tNo>49)
# 
# db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 352)
# 
# subset(db_HR_bio328, trigger> 15 & trigger<72)

db_HR_bio1no328<- db_HR_bio1no328%>%
  arrange(as.numeric(timestart), ssid)

```{r}
db_HR_bio2<- db_HR_bio328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7))
unique(db_HR_bio328$tNo)
```

```{r}
db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
db_HR_bio2<-db_HR_bio1no328

@@

levels(as.factor(db_HR_bio1no328$ssid))
# db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`

#mereg old and new heart rate
# now read them
# db_biohr$trigger
# 
# db_biohr$tno<-db_biohr$trigger
# db_HR_bio2$trigger
# colnames(db_biohr)
# 
# colnames(db_HR_bio2)
# 
# db_biohr$Mean_HR<- db_biohr$HR_BIO
# 
# db_biohr$timestart<- db_biohr$Time
# 
# 
# left_join(db_HR_bio2, db_biohr)

@@

str((db_HR_bio2))
# str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

@@

db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

@@

# db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
# db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
# db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
# db_biohrold2test$ssid<- NULL
# db_HR_bio2$ssid<- NULL

@@

# final
db_HR_bio_final<- db_HR_bio2
db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

# db_HR_bio_final$ssid<- db_HR_bio_final$subj
levels(as.factor(db_HR_bio_final$ssid))

@@

write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355.csv')

db_HR_bio_final$tNo

db_HR_bio_final$tNo

@@

db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)

db_HR_bio_final$BIO

@@

merge heart rate

```{r}
tmp.df4_sum_full_bio$ssid<- as.character(tmp.df4_sum_full_bio$ssid)
db_HR_bio_final$ssid<- as.character(db_HR_bio_final$ssid)

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo'))

@@

Merge self reports

```{r}
tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
